Extended Data

### 2021-10-15 doc/manuscript/Dow_manuscript_Nature.Rmd
discussion

A second possibility is that any additional C fixed during years with warm springs may be allocated, potentially in the following growing season, to plant functions other than stem growth, including respiration, reproduction, foliage, fine roots, or root exudates[@trumbore_quantifying_2002]. 
Stem growth is more sensitive to the water deficits that may be associated with high temperatures than is photosynthesis[@muller_water_2011], and hot or dry conditions have been observed to shift allocation towards roots[@zohner_how_2021], reproduction[**REFS**], or respiration[**REFS**].
Most of this carbon would have a relatively low residence time in the ecosystem[@trumbore_quantifying_2002], although a small fraction would be incorporated into soil organic carbon pools *with residence times rivaling that of wood [REFS]*.
Notably, turnover of extra C fixed during years with warm springs would often occur with sufficient temporal lag that it would not be captured in interannual variation in NEE, implying that the long-term effect of lengthened growing season on NEE may not be captured in studies that consider time frames of a year or less[@zhou_explaining_2016; @fu_maximum_2019].
Studies examining long-term trends in growing season length and ecosystem C uptake[@keeling_increased_1996;@dragoni_evidence_2011;@keenan_net_2014] -- as opposed to their interannual variation -- within or including the temperate deciduous biome showed increasing trends in both variables, suggesting that the C not allocated to current year growth may have a *fairly long* residence time within the ecosystem; however, the amount and fate of this carbon remains unknown.
*BUT SEE @piao_net_2008!! and @barichivich_large-scale_2013 - these are focused on higher latitudes, but shows greater release of C in the fall!*

>>>>

A second possibility is that any additional C fixed during years with warm springs may be allocated, potentially in the following growing season, to plant functions other than stem growth, including respiration, reproduction, foliage, fine roots, or root exudates[@trumbore_quantifying_2002]. 
Stem growth is more sensitive to the water deficits that may be associated with high temperatures than is photosynthesis[@muller_water_2011], and hot or dry conditions have been observed to shift allocation towards roots[@zohner_how_2021], reproduction[@hacket-pain_drought_2017], or respiration[**REFS**].
Most of this carbon would have a relatively low residence time in the ecosystem[@trumbore_quantifying_2002], consistent with studies focused on higher-latitude forests that show enhanced C sequestration in years with warm springs to be offset by higher C losses in the autumn[@piao_net_2008; @barichivich_large-scale_2013].
Notably, though, turnover of extra C fixed during years with warm springs may occur with sufficient temporal lag that it would not be captured in interannual variation in NEE, implying that the long-term effect of lengthened growing season on NEE may not be captured in studies that consider time frames of a year or less[@zhou_explaining_2016; @fu_maximum_2019].
Studies within or including the temperate deciduous biome that examined long-term trends in growing season length and ecosystem C uptake[@keeling_increased_1996;@dragoni_evidence_2011;@keenan_net_2014] -- as opposed to their interannual variation -- showed increasing trends in both variables, suggesting that the C not allocated to woody productivity within the current year growth probably has a residence time of more than a year within the ecosystem; however, the amount and fate of this carbon remains unknown.
